---
title: "R Basics for Business Analysis"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

In this script the basic operations are described and explained. The basic syntax of R is developed around "," (comma) seperations and "()" (bracket) grouping. In general the syntax (grammar of programming language) is similar to 
```{r}
object <- function(parameter1, vector2, dataframe3)
```
In which is an object is the "thing" in which results can be stored, the function is something by which the information is processed (usually relates to a library), a parameter which is this case is a value, a vector which is the same as a variable (a sequence of values) and a dataframe which is identical to a flat-table (just like a sheet in excel is). Good to know is that R has simmplified datastructures that are all compatable with each other. 

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
